A model-based method for measuring stability in personal culture with panel data[^thanks]

### 2020-12-19 ms_anonymized.Rmd
separated normal and anonymous version

---
title: A model-based method for measuring stability in personal culture with panel data[^thanks]
author:
  - Stephen Vaisey, Duke University
  - Kevin Kiley, Duke University
date: "12/16/2020"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
    number_sections: true
bibliography: ["panel-change-sem.bib"]
header-includes:
  - \usepackage{setspace}\onehalfspacing
mainfont: Minion Pro
fontsize: 11pt
---

>>>>

---
title: A model-based method for measuring stability in personal culture with panel data[^thanks]
date: "12/19/2020"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
    number_sections: true
bibliography: ["panel-change-sem.bib"]
header-includes:
  - \usepackage{setspace}\onehalfspacing
mainfont: Minion Pro
fontsize: 12pt
---
